Reasoning About a Machine with Local Capabilities

### 2019-02-10 toplas/paper.tex
[TOPLAS] Add secure compilation reference

If we want to scale this approach even further, we would like to reason at a
higher level of abstraction namely at the level of a high-level language.
That is, we would rather construct a program logic for a high-level language, so
we can reason about the programs the language we actually write them in and at
the same time get the guarantees for the programs we are going to execute, i.e.\
the compiled programs. To achieve this, we would have to construct a secure compilation that preserves the security abstraction of the high-level language. Our logical relation would not be directly applicable in a secure compilation proof, the experiences made from constructing a logical relation for a capability machine can still be used.
\end{toplas}
\itoplassug{We could further add that this is not the level of abstraction that
  one would like to reason. One would like to reason about the programs we
  actually write - that is programs written in high-level languages. If we had a
  fully-abstract compiler from a nice high-level language to this low-level
  machine, then we could reason about the program in the high-level language and
  then because the compiler is fully-abstract, we would retain all the nice
  properties from the high-level language. How does this work fit in to this
  picture? The calling convention ensures two properties that we expect our nice
  high-level languages to have, namely well-bracketedness and local-state
  encapsulation. If we want to do fully-abstract compilation, then we need some
  way to guarantee this after compilation. Further, logical relations are often
  used in full-abstractness proofs. This work expands our knowledge about
  logical relations should be defined for low-languages and in particular
  capability machines. (maybe also mention that enforcement necessary for
  fully-abstract compilation. Could be capability, but it could also be
  something else - we just need something which we do not have now.) }

>>>>

If we want to scale this approach even further, we would like to reason at a
higher level of abstraction namely at the level of a high-level language.
That is, we would rather construct a program logic for a high-level language, so
we can reason about the programs the language we actually write them in and at
the same time get the guarantees for the programs we are going to execute, i.e.\
the compiled programs. To achieve this, we would have to construct a secure
compilation \citep{patrignani_secure_compilation_2019} that preserves the security abstraction of the high-level language. Our logical relation would not be directly applicable in a secure compilation proof, the experiences made from constructing a logical relation for a capability machine can still be used.
\end{toplas}
\itoplassug{We could further add that this is not the level of abstraction that
  one would like to reason. One would like to reason about the programs we
  actually write - that is programs written in high-level languages. If we had a
  fully-abstract compiler from a nice high-level language to this low-level
  machine, then we could reason about the program in the high-level language and
  then because the compiler is fully-abstract, we would retain all the nice
  properties from the high-level language. How does this work fit in to this
  picture? The calling convention ensures two properties that we expect our nice
  high-level languages to have, namely well-bracketedness and local-state
  encapsulation. If we want to do fully-abstract compilation, then we need some
  way to guarantee this after compilation. Further, logical relations are often
  used in full-abstractness proofs. This work expands our knowledge about
  logical relations should be defined for low-languages and in particular
  capability machines. (maybe also mention that enforcement necessary for
  fully-abstract compilation. Could be capability, but it could also be
  something else - we just need something which we do not have now.) }
